Gradual Soundness: Lessons from Static Python

### 2022-01-14 pj-7.1/paper.tex
pj: sec 4, example spec error caught

\subsection{The Payoff: Issues Reported}
%% 2022-01-11 FILL TODO reword, excitement!

@@

@@

>>>>

\subsection{The Payoff: Issues Reported}

@@

For example, we discovered that \SP{} handled the following function incorrectly when
we tried to model it:
%% \url{https://github.com/facebookincubator/cinder/issues/62}

\medskip
\begin{minipage}[t]{0.25\columnwidth}~
\end{minipage}\begin{minipage}[t]{0.4\columnwidth}
\begin{lstlisting}
  from typing import Optional

  def f(x: Optional[str]) -> str:
    while True:
      if x is None:
        break
      return x

  print(f(None))
  # None
\end{lstlisting}
\end{minipage}

\noindent{}The function expects either a string or the \code{None} value and promises to return a string.
When called with \code{None}, however, the function breaks out of the \code{while} loop
and implicitly returns \code{None}---disobeying the return type.
\SP{} had failed to account for the \code{break} and implicit return.
More concerningly, the associated test case \emph{expected} the program to type check.
Creating a formal model helped us catch this specification error.

@@

Concrete types
